---
title: "week6_codealong"
author: "Genevieve Chiong"
date: "11/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```


```{r}
hist(gp_1)
```

```{r}
hist(gp_2)
```

```{r}
my_mwu <- wilcox.test(gp_1, gp_2)
```


```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point()
```


```{r}
# Linear model, stored as penguin_lm: 
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

# Return the complete overview:
summary(penguin_lm)
```


```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)
```

```{r}
# Get the intercept:
penguin_int <- penguin_lm_tidy$estimate[1]
penguin_int
```

```{r}
# Then to get the flipper_length coefficient:
penguin_coef <- penguin_lm_tidy$estimate[2]
penguin_coef
```

```{r}
# Metrics at a glance:
penguin_lm_out <- broom::glance(penguin_lm)
penguin_lm_out
```

"Simple linear regression was used to explore the relationship between penguin flipper length (mm) and body mass (g) across all three penguin species, and including both male and female penguins. A significant regression model was found ($\beta$ = `r round(penguin_coef,3)`, F(`r penguin_lm_out$df`,`r penguin_lm_out$df.residual`) = `r round(penguin_lm_out$statistic,1)`, p < 0.001) with an R^2^ of `r round(penguin_lm_out$r.squared,3)`."

```{r}
# Use the plot() function on the model, which will automatically create four useful visualizations to consider assumptions! 

plot(penguin_lm)
```

## The first one: fitted values vs. residuals
## The second one: QQ-plot for residuals
## The third one: another way of looking at fitted vs. residuals (these are just standardized residuals, but you can interpret it the same way)
## The fourth one: Cook’s distance, a measure of “influence” or “leverage” that individual points have on the model - often considered a way to explore outliers.
See the Week 6 Part 2 Lecture video for more information about how to interpret these outcomes, but in summary: graphs 1 & 3 are useful for thinking about homoscedasticity; graph 2 (QQ plot) helps us consider normality of residuals; graph 4 reveals the Cook’s distance (a measure of how much leverage any single observation has on the model).

```{r}
# Use geom_smooth(method = "lm") to add a linear model to an existing scatterplot
# Use stat_cor() and/or stat_regline_equation() to add equation information directly to the plot panel, and at an x- and y- position that you specify (and yes, you can mess with the digits & appearance here)

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(size = 2) + 
  geom_smooth(method = "lm",
              color = "red", 
              size = 0.5, 
              fill = "gray10", 
              alpha = 0.5) +
  theme_light() + 
  ggpubr::stat_regline_equation(label.x = 180, label.y = 5700)
```

```{r}
# We'll use the cor.test() function, adding the two vectors (flipper_length_mm and body_mass_g) as the arguments. The function reports the Pearson's r value, and performs a hypothesis test with null hypothesis that the correlation = 0. 

penguins_cor <- cor.test(penguins$flipper_length_mm, penguins$body_mass_g)
```

Here, we see that there is a strong positive correlation between penguin flipper length and body mass (*r* = `r round(penguins_cor$estimate,2)`, t(`r penguins_cor$parameter`) = `r round(penguins_cor$statistic,2)`, p < 0.001). 






